### 2023-10-11 main.tex
Remove mapping

	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}

@@

	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}

@@

	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N

@@

	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}

@@

	\Gamma(2+L)

@@

	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle

@@

	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}

@@

|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle

@@

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}

@@

@@

  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)

@@

		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

 \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

\section{Mapping to equilibrium} \label{Section-Mapping}
{\color{red}check also Appendix A in
\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}} \\
In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. These diagonal boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium.
This can be represented by the diagram 
	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
Namely, the following equation holds true
	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
The eigenvectors and the eigenvalues of $H_{0}$ have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$
	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 
\subsection{The non local transformation}\label{SectionNonLocalTrasformation}
We define the equilibrium Hamiltonian as
	H^{0}=H_{left}^{0}+H_{bulk}+H^{0}_{right}
	H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{0}=e_{NN}^{L}-\mathbbm{1}^{L}
Therefore we have that
	H^{''}=H^{0}+H^{B}
	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
We look for a matrix $W$ such that 
\begin{equation}\label{GoalWH}
	H^{''}W=WH_{0}
 We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e. $m_{i}$ indicates the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$. We denote by $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We prove that 
\begin{equation}\label{W-extended}
	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
\paragraph{Construction of the matrix W}
We aim to show that \eqref{W-extended} fulfils \eqref{GoalWH}. Consider the \textit{resolvent operator}
	\mathcal{R}(z,H^{''}):=\left(z-H^{''}\right)^{-1}
where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the $\mathcal{R}(x,H^{''})$ is well defined. 
The above equation implies that 
	(z-H^{''})\mathcal{R}(H^{''},z)=I
In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix an arbitrary $\epsilon>0$ and consider $z=\mathcal{E}_{\bm{m}}+\epsilon$, 
	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1
We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
by summing over all possible $\bm{m}$'s such that $|\bm{m}|=L$ and multiply by $\epsilon$ both sides
%	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
%we multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
We take the limit for $\epsilon\to 0$ on both sides 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We first observe that
	\lim_{\epsilon\to 0}\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)=\left(\Lambda_{\bm{m}}-H^{''}\right)<\infty
Second, using the power expansion
\begin{equation}\label{veryUsefulSeries}
	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
we have that, for each $\bm{m}$, 
		&\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\mathcal{E}_{\bm{m}}+\epsilon)^{-1}H^{''}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\mathcal{E}_{\bm{m}}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-\mathcal{E}_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
Since both factor are finite, the limit of the product is the product of the limit and we obtain
	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
Since the limit of the sum is the sum of the limit   
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Recalling that $|\Psi_{\bm{m}}^{0}\rangle$ are the eigenvectors with eigenvalue $\mathcal{E}_{\bm{m}}$ of $H_{0}$ we have 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Since $H_{0}=H_{0}^{T}$ 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
By calling 
	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
	WH_{0}=H^{''}W
Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}). Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression allows a simpler treatment of the mapping and also allows to  find a closed formula for the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To achieve this aim, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}). In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$ situation. 
\subsection{Quantum inverse scattering method}\label{SubsectionQISM}
We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$. In the case of the multi-species stirring process we chose $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
	R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
and the $K$-matrices
		\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
		K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
\begin{equation}\label{KmatrixHAT}
	\widehat{K}_{a}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
		1-x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		0&0&\ldots&1+x
\begin{equation}\label{Kmatrix}
	K_{a}(x)=\frac{\left((2x+N)H^{''}_{left}+(x+N)I\right)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		0&0&0&\ldots&0&N+x
where the lower index $a\in\{0,\ldots,L\}$ means that these matrices are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$. Variables $x,y\in\mathbb{C}$ are called spectral parameters.  
The matrices $R_{a,b}(x)$, $K_{a}(x)$ and $\widehat{K}_{a}(x)$ satisfy:
\begin{itemize}
	\item \textit{Yang-Baxter-Equation}
		R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
	\item \textit{Boundary-Yang-Baxter-Equation}
		R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
	\item \textit{Dual Boundary-Yang-Baxter-Equation}
		K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
\end{itemize}
We introduce the \textit{transfer matrix}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
that satisfies
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(x))\lvert_{x=0}=C_{1}H^{''}+C_{2}I
with $C_{1},C_{2}>0$. \\
The matrix $U_{0}(x)$ used to construct $T(x)$ is called double row monodromy and it is given by
	U_{0}(x)=M_{0}(x)\widehat{K}_{0}(x)\widehat{M}_{0}(x)
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}(x)=R_{0L}(x)\ldots R_{01}(x)
$U_{0}(x)$ satisfies the following relation
\begin{equation}\label{RURU}
	R_{ab}(x-y)U_{a}(x)R_{ab}(x+y)U_{b}(y)=U_{b}(y)R_{ab}(x+y)U_{a}(x)R_{ab}(x-y)
 $U_{0}(x)$ can be written in the canonical basis of $V_{0}$ 
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			\vdots&\vdots&\ddots&\vdots\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
\begin{equation}\label{matrixForm-U}
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
where each of the above element acts on the quantum space $V$. Using \eqref{RURU}, we find some \textit{exchange relations} that the elements of $U_{0}(x)$ must satisfy: 
\begin{itemize}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
	\begin{equation}\label{EX2}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
\item for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
\begin{equation}\label{EX4}
		D_{i,j}(x)B_{i}(y)=&-(x-y)h_{1}(x,y)B_{i}(y)D_{i,j}(x)+f_{2}(x,y)\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(y)D_{k,j}(x)\\+&\frac{1}{(x-y)}\left(B_{j}(y)D_{i,i}(x)-B_{j}(x)D_{i,i}(y)\right)\\+&\frac{1}{2}h_{3}(x,y)\left((1+x-y)B_{j}(x)D_{N,N}(y)-B_{j}(y)D_{N,N}(x)\right)
\begin{equation}\label{EX5}
	D_{i,j}(x)B_{j}(y)=\frac{(x-y)}{(x-y-1)}B_{j}D_{i,j}(x)+\frac{1}{(y+1-x)}D_{i,j}(y)B_{j}(x)
\item  for every $i,j,k\in \{1,\ldots,N-1\}$ such that $i\neq j\neq k$
\begin{equation}\label{EX6}
	D_{i,j}(x)B_{k}(y)=B_{k}(y)D_{i,j}(x)+\frac{1}{(x-y)}\left(B_{k}(y)D_{j,i}(x)-B_{k}(x)D_{j,i}(y)\right)
\end{itemize}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\subsection{Charges}
Using the matrix form of $U_{0}(x)$ \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
		T(x)=%tr_{0}&\left(\begin{pmatrix}
			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		%	0&0&0&\ldots&0&N+x
	%	\end{pmatrix}\right.
	%	\;\;\;\begin{pmatrix}
	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	%	\end{pmatrix}\right)\\
	%=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
By construction, $T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$, i.e. 
		T(x)=
		\sum_{k=0}^{2L+2}Q^{k}x^{k}
where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q^{k}$ the \textit{conserved charges} of the system. 
We also introduce 
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
Arguing similarly, we also write the elements of $U_{0}(x)$ as polynomials in $x$ 
	D_{N,N}(x)=\sum_{k=0}^{2L+1}D_{N,N}^{k}x^{k}\quad D_{i,i}(x)=\sum_{k=0}^{2L+1}D_{i,i}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}\quad D_{i,j}(x)=\sum_{k=0}^{2L}D_{i,j}^{k}x^{k}
We will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three conserved charges of the systems. As a consequence, we will compute only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 
\begin{itemize}
	\item For $D_{N,N}(x)$: 
	D_{N,N}^{2L+1}=I^{tot}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}

>>>>

	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}\dt

@@

	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}\dt

@@

	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N\co

@@

	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}\dt

@@

	\Gamma(2+L)\dt

@@

	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle\dt

@@

	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\dt

@@

|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle\dt

@@

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt

@@

  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt

@@

		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt

@@

=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt

@@

 \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt

@@

\section{Extensions for the non-integrable chain}
In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using to integrability.  
The aim of this section is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
\begin{enumerate}
	%\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average densities evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is also proved. Subsection \ref{Subsection-RD}
\end{enumerate}
